The document title

### 2021-03-08 manuscript/manuscript.Rmd
Begin the Results section

@@

# References

>>>>

\section*{Results}

```{r bmi_class}
BMI_avg <- sample_descriptives$BMI_mean
BMI_class <- NA
if (BMI_avg >= 18.5 & BMI_avg < 25) {
  BMI_class <- "normal weight"
} else if (BMI_avg >= 25 & BMI_avg < 30) {
  BMI_class <- "overweight"
} else if (BMI_avg >= 30 & BMI_avg < 35) {
  BMI_class <- "obesity class I"
} else if (BMI_avg >= 35 & BMI_avg < 40) {
  BMI_class <- "obesity class II"
} else if (BMI_avg >= 40) {
  BMI_class <- "obesity class III"
}
```
Our recruited sample presented an average BMI of `r sample_descriptives$BMI_mean` $\mathrm{kg\cdot m^{-2}}$, which is relatively high and classified as `r BMI_class`. 
It would be expected that participants with higher BMI values, due to low motor ability and physical capacity, are able to perform the trials only at the lowest speeds.
This is precisely what happened and, as can be observed in Figure 1, from 2 to 5 $\mathrm{km\cdot h^{-1}}$ the BMI median is around 30 $\mathrm{kg\cdot m^{-2}}$, decreasing to around 27 $\mathrm{kg\cdot m^{-2}}$ at 6 $\mathrm{km\cdot h^{-1}}$, which is the fastest walking speed, with a further reduction to less than 25 $\mathrm{kg\cdot m^{-2}}$ at the running speeds. Furthermore, only one participant with a BMI higher than 30 $\mathrm{kg\cdot m^{-2}}$ was able to run. This implies in a sample size reduction from `r filter(sample_size, acc_placement == "hip" & vector == "resultant" & speed == "2")$pGRF_N` at the slowest speed to `r filter(sample_size, acc_placement == "hip" & vector == "resultant" & speed == "14")$pGRF_N` at the fastest.

\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{fig1.png}
		\caption{Distribution of participant’s body mass index per speed. Dots represent individual participants.}
	\end{measuredfigure}
\end{figure}

As the main variables collected in this experiment are the peak magnitudes and rates of the GRF and ACC signals, there was a need to first establish their relationship. During locomotion, pACC increases linearly as pGRF increases. Such relation can be observed in the Figure 2, Panel A, for from hip-worn accelerometers and the resultant vector, and in Supplemental Figure S1 for all placements and the resultant vector and its vertical component. Moreover, for the same pACC values, the registered pGRF tended to be higher in subjects with higher BMI. It demonstrates that accelerometer data can adequately discriminate between different BMI categories. However, data from the pAR x pLR relationship show a greater dispersion, especially at higher values, and cannot discriminate so well the different BMI categories, as can be observed in Figure 2, Panel B, and Supplemental Figure S2.

\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{fig2.png}
		\caption{Relationship between variables collected by force plates and accelerometers worn at hip, for the resultant vector. Linear trends for each body mass index category are also depicted. Panel A shows peak magnitudes (pRGRF and pRACC) while Panel B shows peak rates (pRLR and pRAR). Abbreviations: pRACC, peak resultant acceleration; pRAR, peak resultant acceleration rate; pRGRF, peak resultant ground reaction force; pRLR, peak resultant loading rate.}
	\end{measuredfigure}
\end{figure}

@@

\section*{References}

<div id="refs"></div>

\section*{Supplemental Material}

\subsection*{Supplemental Figure S1}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS1.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Relationship between peak ground reaction force and acceleration magnitudes. Data from accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Linear trends for each body mass index category are also depicted. Abbreviations: pRACC, peak resultant acceleration; pRGRF, peak resultant ground reaction force; pVACC, peak vertical acceleration; pVGRF, peak vertical ground reaction force.

\subsection*{Supplemental Figure S2}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS2.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Relationship between peak loading and acceleration rates. Data from accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Linear trends for each body mass index category are also depicted. Abbreviations: pRAR, peak resultant acceleration rate; pRLR, peak resultant loading rate; pVAR, peak vertical acceleration rate; pVLR, peak vertical loading rate.
